---
title: "Replikaatio"
author: "Annika Lehmus-Sun"
output: html_document
---
#REPLIKOITAVA TUTKIMUS JA ANALYYSI
Tutkimus: anand et al. toimintamahdollisuuksien teoria, alkuperäinen julkaistu artikkeli analyysista löytyy täältä: [Anand et al.](http://philosophy.uchicago.edu/faculty/files/nussbaum/Capabilities%20and%20Well-Being%20Evidence%20Based%20on%20the%20Sen-Nussbaum%20Approach%20to%20Welfare.pdf)

#AINEISTO JA MUUTTUJAT
to use data for the analysis from the British Household Panel Survey (BHPS), an annual survey of each adult (16+) member of a nationally representative sample of more than 5000 households, comprising a total of approxi- mately 10 000 individual interviews. The survey presents a major collaboration between statisticians and social scientists, is constantly revised and can reasonably be taken as reflecting good practice in terms of questionnaire design. The main method of data collection at each wave is by face-to-home in-home interviewing and this paper draws on data from the 10th wave of interviews carried out in the year 2000.

British household panel Survey [BHPS] vuosi 2000. Lisätietoa aineistosta löydät täältä: [BHPS 2000](https://www.iser.essex.ac.uk/bhps/documentation/pdf_versions/index.html) ja yleistä BHPS:stä: [British household panel survey](https://www.iser.essex.ac.uk/bhps)
Anand. et al. käyttivät analyysissaan seuraavia muuttujia: 

###Muuttujalista: 
1. **S_HL_LIMIT** Does your health in any way limit your daily activities compared to most people of your age?
2. **S_HL_NOURISH** Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Eat meat, chicken, fish every second day) 
 + 2a.  Would you like to be able to eat meat, chicken, fish at least every second day, but must do without because you cannot afford it?
3. **S_H_LAC_MOVE** If you could choose, would you stay here in your present home or would you prefer to move somewhere else?
  + 3a. Even though you may not want to move) Do you expect you will move in the coming year?
5. **S_S_CAR** Do you normally have access to a car or van that you can use whenever you want to?
6. **S_H_CRIME** Does your accommodation have any of the following problems? Vandalism or crime in the area
7. **S_S_EDUCATE** Education
8. **S_W_CONCB**; **S_W_CONCL**; **S_W_CONCML** Have you recently been able to concentrate on whatever you’re doing (‘Better than usual’;‘Less than usual’;‘Much less than usual)
9. **S_W_SLEEPN**; **S_W_SLEEPM**; **S_W_SLEEPMM** Have you recently lost much sleep over worry?('Not at all’; ‘Rather more than usual’; 'Much more than usual')
10. **S_W_STRAINN**; **S_W_STRAINM**; **S_W_STRAINMM**  Have you recently felt constantly under strain? ('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
11. **S_W_DEPRESSN**; **S_W_DEPRESSM**; **S_W_DEPRESSMM** Have you recently been feeling unhappy or depressed? ('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
12. **S_W_CONFIDENTN**; **S_W_CONFIDENTM**; **S_W_CONFIDENTMM** Have you recently been losing confidence in yourself? ('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
13. **S_W_DECIDEM**; **S_W_DECIDEL**; **S_W_DECIDEML** Have you recently felt capable of making decisions about things? ('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
14. **S_W_DIFICULTN**; **S_W_DIFICULTM**; **S_W_DIFICULTMM** Have you recently felt you couldn’t overcome your difficulties?('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
15. **S_W_FACEUPM**; **S_W_FACEUPL**; **S_W_FACEUPMML** Have you recently been able to face up to problems?('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
16. **S_S_HOLIDAY** Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Pay for a week’s annual holiday away from home.
 + 16a. Would you like to be able to pay for a week’s annual holiday away from home, but must do without because you cannot afford it?
17. **S_S_CLOTHES** Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Buy new, rather than second hand, clothes.
 + 17a Would you like to be able to buy new, rather than second hand, clothes, but must do without because you cannot afford it?
18. **S_S_MEAL** Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Have friends or family for a drink or meal at least once a month
 +18a. Would you like to be able to have friends or family for a drink or meal at least once a month, but must do without because you cannot afford it?
19. **S_W_WORTHN**; **S_W_WORTHM**; **S_W_WORTHMM** Have you recently been thinking of yourself as a worthless person? ('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
20. **S_W_ROLEM**; **S_W_ROLEL**; **S_W_ROLEML** Have you recently felt that you were playing a useful part in things?('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
21. **S_W_HAPPYM**; **S_W_HAPPYL**; **S_W_HAPPYML** Have you recently been feeling reasonably happy, all things considered?('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
22. **S_W_EACTIVEM**; **S_W_EACTIVEL**; **S_W_EACTIVEML** Have you recently been able to enjoy your normal day- to-day activities?('Not at all’;‘Rather more than usual’; ‘Much More than usual’)
23. **S_VOTE** Did you vote in this (past) year’s general election?
24. **S_HL_PWORK**;**S_HL_NAWORK** Does your health keep you from doing some types of work? ('Yes'; 'Can do nothing')
25. **S_HL_AWORKL**; **S_HLAWORKLTL**; **S_HLAWORKS**  For work you can do, how much does your health limit the amount of work you can do? ('A lot'; 'Just a little'; 'Somewhat')
26. **S_OALL** How dissatisfied or satisfied are you with your life overall?
27. **S_HEALTH** How dissatisfied or satisfied are you with your health?
28. **S_H_INCOME** How dissatisfied or satisfied are you with the income of your household?
29. **S_HOUSE** How dissatisfied or satisfied are you with your house/flat?
30. **S_PARTNER2** How dissatisfied or satisfied are you with your husband/ wife/partner?
31. **S_JOB2** How dissatisfied or satisfied are you with your job?
32. **S_SOCIAL** How dissatisfied or satisfied are you with your social life?
33. **S_QLEISURE** How dissatisfied or satisfied are you with the amount of leisure time you have?
34. **S_LEISURE** How dissatisfied or satisfied are you with the way you spend your leisure?

Taustamuuttujat (ks. kohta puuttuvat tiedot)
**C** gender
**D_NOPARTNER** S_partner - does not apply
**D_NOJOB** S_job2 - does not apply


###Muuttujamuutokset
Muuttujamuunnokset, jotka ovat tehty Anand et. al.:in analyysin pohjalta ja mukaisesti löytyvät täältä: [muuttujamuunnokset](https://github.com/AnnikaLehmusSun/replikaatio/blob/master/data/muuttujamuunnokset.R)

--> kaikkia muuttujia ei ole selitetty, ja koodattu vaikeasti, sekottaa?

####Puuttuvat tiedot
tämähän kannattaa nyt kirjata raporttiin – tutkimusta ei voi täysin varmasti toistaa, kun ei ole kerrottu mitä puuttuville
tiedoille on tehty, ja päättää itse miten etenet –eli varmaan tuo NA on loogisin oletus.

Anand et al. käyttivät taustamuuttujina uudelleennimeämiään muuttujia: D_NOJOB, D_NOPARTNER ja C. He eivät kuitenkaan missään kohdin kertoneet tarkemmin, mistä BHPS muuttujista näissä on kyse. Tässäkin kohdassa joutui hieman ollettamaan ja tekemään itsenäisiä päätöksiä. Oletin siis, että BHPS muuttujista JSEX = C; JMASTAT (marital status) arvot > 3 = D_NOPARTNER; ja JJBSTATT (employment status on Sept. 1 this year [2000]) arvot > 2 = D_NOJOB. 
etenkin parisuhdetta ja työtä käsitteleviä kysymyksiä oli useampi, joten ei ole varmuutta siitä, mitä muuttujia Anand et al. näissä kohdin käyttivät, mikä heikentää niin ikään tutkimuksen toistettavuutta. 

#REPLIKAATIO
```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(haven, ggplot2,knitr, pander,descr,foreign,dplyr,Hmisc,psych,GPArotation,plyr, dplyr, rmarkdown)
BHPS_naiset <- read.csv(file = "/Applications/replikaatio/data/BHPS_naiset.csv", sep=",", header =TRUE)
dim(BHPS_naiset)
BHPS_miehet <- read.csv(file = "/Applications/replikaatio/data/BHPS_miehet.csv", sep=",", header =TRUE)
dim(BHPS_miehet)
BHPS_naiset$X <- NULL
BHPS_miehet$X <- NULL
```

##Malli 1
####Overall satisfaction regressed on elements of satisfaction (model 1) – females
```{r, echo=FALSE}
library(GGally)
library(ggplot2)
model1F <- lm(S_OALL ~ D_NOJOB + D_NOPARTNER + S_HEALTH + S_HOUSE + S_H_INCOME + S_PARTNER2 + S_JOB2 + S_SOCIAL + S_LEISURE + S_QLEISURE, data = BHPS_naiset)
summary(model1F)
```
####Overall satisfaction regressed on elements of satisfaction (model 1) – males
```{r}
model1M <- lm(S_OALL ~ D_NOJOB + D_NOPARTNER + S_HEALTH + S_HOUSE + S_H_INCOME + S_PARTNER2 + S_JOB2 + S_SOCIAL + S_LEISURE + S_QLEISURE, data = BHPS_miehet)
summary(model1M)
```

### residuaalit malliin 2 ja 3
sivun 20 alalaidan kuvauksen perusteella tulkitsen, että he ovat ensin tehneet 10 regressiota, yhden jokaiselle tyytyväisyyden osa-alueille (kuvaus s. 18), joissa selittäjinä on capabilities, ja tallentaneet tuosta residuaalit aineistoon, ja käyttävät niitä alkuperäisten muuttujien sijasta: siis vaikka tyytyväisyys sosiaaliseen elämään -kysymys mittaa oikeastaan tyytyväisyyttä SEKÄ persoonallisuutta, ja regressiolla yritetään siivota tuo persoonallisuuden osuus pois, jotta saadaan puhdas tyytyväisyys-mittari.
malli$residuals (vai onkohan $resids) sisältää nämä, ja voit siis liittää muuttujaksi aineistoon
ihan normaalisti 
(aineisto$resid_social <- malli_social$residuals) tms.
varmuudeksi: nuo residuaalit eivät siis tule noista ensimmäisistä malleista, vaan ensin tehdään 10 regressiomallia, joissa selitettävänä on vuorollaan kukin osa-aluetyytyväisyyksistä.
miksi BHPS$RESIDF <- model1F$residuals ei toiminut?  Voisit kokeilla modelr-paketin add_residuals() -funktiota, se ainakin osaa ottaa huomioon puuttuvat tiedot.

### 10 regressiomallia + residuaalit, naiset
```{r}

model1F_DNOJOB <- lm(D_NOJOB ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_DNOJOB)

model1F_DNOPARTNER <- lm(D_NOPARTNER ~  S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_DNOPARTNER)

model1F_HEALTH <- lm(S_HEALTH ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_HEALTH)

model1F_HOUSE <- lm(S_HOUSE ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_HOUSE)

model1F_H_INCOME <- lm(S_H_INCOME ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_H_INCOME)

model1F_PARTNER2 <- lm(S_PARTNER2 ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_PARTNER2)

model1F_JOB2 <- lm(S_JOB2 ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_JOB2)

model1F_SOCIAL <- lm(S_SOCIAL ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_SOCIAL)

model1F_SOCIAL <- lm(S_SOCIAL ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_SOCIAL)


model1F_LEISURE <- lm(S_LEISURE  ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_LEISURE)

model1F_QLEISURE <- lm(S_QLEISURE ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_naiset)
summary(model1F_QLEISURE)
```
### regressiomallit x 10, miehet
```{r}
model1M_DNOJOB <- lm(D_NOJOB ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_DNOJOB)

model1M_DNOPARTNER <- lm(D_NOPARTNER ~  S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_DNOPARTNER)

model1M_HEALTH <- lm(S_HEALTH ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_HEALTH)

model1M_HOUSE <- lm(S_HOUSE ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_HOUSE)

model1M_H_INCOME <- lm(S_H_INCOME ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_H_INCOME)

model1M_PARTNER2 <- lm(S_PARTNER2 ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_PARTNER2)

model1M_JOB2 <- lm(S_JOB2 ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_JOB2)

model1M_SOCIAL <- lm(S_SOCIAL ~S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_SOCIAL)

model1M_LEISURE <- lm(S_LEISURE  ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_LEISURE)

model1M_QLEISURE <- lm(S_QLEISURE ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS, data = BHPS_miehet)
summary(model1M_QLEISURE)
```

    
### tallennetaan residuaalit omiksi tiedostoiksi
```{r}
#naiset ensin
library(modelr)

BHPS_naiset <- add_residuals(data=BHPS_naiset, model=model1F_DNOJOB, var="RESIDF_DNOJOB")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_DNOPARTNER, var="RESIDF_DNOPARTNR")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_HEALTH, var="RESIDF_HEALTH")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_HOUSE, var="RESIDF_HOUSE")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_H_INCOME, var="RESIDF_H_INCOME")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_PARTNER2, var="RESIDF_PARTNER")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_JOB2, var="RESIDF_JOB")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_SOCIAL, var="RESIDF_SOCIAL")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_LEISURE, var="RESIDF_LEISURE")
BHPS_naiset <-add_residuals(data=BHPS_naiset, model=model1F_QLEISURE, var="RESIDF_QLEISURE")


#sitten miehet
BHPS_miehet <- add_residuals(data=BHPS_miehet, model=model1M_DNOJOB, var="RESIDM_DNOJOB")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_DNOPARTNER, var="RESIDM_DNOPARTNR")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_HEALTH, var="RESIDM_HEALTH")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_HOUSE, var="RESIDM_HOUSE")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_H_INCOME, var="RESIDM_H_INCOME")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_PARTNER2, var="RESIDM_PARTNER")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_JOB2, var="RESIDM_JOB")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_SOCIAL, var="RESIDM_SOCIAL")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_LEISURE, var="RESIDM_LEISURE")
BHPS_miehet <-add_residuals(data=BHPS_miehet, model=model1M_QLEISURE, var="RESIDM_QLEISURE")

```

##Malli 2 PROBLEM WITH NOJOB AND NOPARTNER -VARIABLES
Mallissa 2 Anand et al. ovat lisänneet metodilla (x?) personallisuuteen liittyvät tekijät, eli katsoneet millä tavoin eri tekijät korreloivat keskenään, ja lisänneet ne malleihin 2 ja 4. Tässä työssä päätin kuitenkin keskittyä vain malliin 1 ja 3, jotka ovat  tehty ilman personaan vaikutusta, sillä näidenkin analyysien toistaminen on tarpeeksi uskoakseni! Anand et al. jättivät myös itse mallin 4 ulkopuolelle, pitkälti tilan puutteen vuoksi tosin. 


####Overall satisfaction regressed on elements of satisfaction and personality traits (model 2) – females
```{r}
model2F <- lm(S_OALL ~ D_NOJOB + D_NOPARTNER + S_HEALTH + S_HOUSE + S_H_INCOME + S_PARTNER2 + S_JOB2 + S_SOCIAL + S_LEISURE + S_QLEISURE + RESIDF_DNOJOB + RESIDF_DNOPARTNR + RESIDF_HEALTH + RESIDF_HOUSE + RESIDF_H_INCOME + RESIDF_PARTNER + RESIDF_JOB + RESIDF_SOCIAL + RESIDF_LEISURE + RESIDF_QLEISURE, data = BHPS_naiset)
summary(model2F)

```

###Overall satisfaction regressed on elements of satisfaction and personality traits (model 2) – males

```{r}
model2M <- lm(S_OALL  ~ D_NOJOB + D_NOPARTNER + S_HEALTH + S_HOUSE + S_H_INCOME + S_PARTNER2 + S_JOB2 + S_SOCIAL + S_LEISURE + S_QLEISURE + RESIDM_DNOJOB + RESIDM_DNOPARTNR + RESIDM_HEALTH + RESIDM_HOUSE + RESIDM_H_INCOME + RESIDM_PARTNER + RESIDM_JOB + RESIDM_SOCIAL + RESIDM_LEISURE + RESIDM_QLEISURE, data = BHPS_miehet)
summary(model2M)
```


##Malli 3
Overall satisfaction regressed on capabilities and personality traits (model 3) – females

```{r}
model3F <- lm(S_OALL ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS + RESIDF_DNOJOB + RESIDF_DNOPARTNR + RESIDF_HEALTH + RESIDF_HOUSE + RESIDF_H_INCOME + RESIDF_PARTNER + RESIDF_JOB + RESIDF_SOCIAL + RESIDF_LEISURE + RESIDF_QLEISURE, data = BHPS_naiset)
summary(model3F)
```

Overall satisfaction regressed on capabilities and personality traits (model 3) – males
```{r}
model3M <- lm(S_OALL ~ S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE +S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS + RESIDM_DNOJOB + RESIDM_DNOPARTNR + RESIDM_HEALTH + RESIDM_HOUSE + RESIDM_H_INCOME + RESIDM_PARTNER + RESIDM_JOB + RESIDM_SOCIAL + RESIDM_LEISURE + RESIDM_QLEISURE, data = BHPS_miehet)
summary(model3F)
```

#TULOKSET

#LÄHTEET
Anand, P., Hunter, G., & Smith, R. (2005). Capabilities and Well-Being: Evidence Based on the Sen–Nussbaum Approach to Welfare. Social Indicators Research, 74(1), 9–55. https://doi.org/10.1007/s11205-005-6518-z

British Household Panel Survey, wave 10, Economic and Social Research Council Research Centre on Micro-Social Change, Essex: UK Data Archive (distributor)

#Just in case
#capabilities: 
S_HL_Limit + S_HL_NOURISH + S_H_LAC_MOVE + S_S_CAR + S_H_CRIME + S_S_EDUCATE + S_W_CONCB + S_W_CONCL + S_W_CONCML + S_W_SLEEPN + S_W_SLEEPM + S_W_SLEEPMM + S_W_STRAINN + S_W_STRAINM + S_W_STRAINMM + S_W_DEPRESSN + S_W_DEPRESSM + S_W_DEPRESSMM + S_W_CONFIDENTN + S_W_CONFIDENTM + S_W_CONFIDENTMM + S_W_DECIDEM + S_W_DECIDEL + S_W_DECIDEML + S_W_DIFICULTN + S_W_DIFICULTM + S_W_DIFICULTMM + S_W_FACEUPM + S_W_FACEUPL + S_W_FACEUPL + S_S_HOLIDAY + S_S_CLOTHES + S_S_MEAL + S_W_WORTHN + S_W_WORTHM + S_W_WORTHMM + S_W_ROLEM + S_W_ROLEL + S_W_ROLEML + S_W_HAPPYM + S_W_HAPPYL + S_W_HAPPYML + S_W_EACTIVEM + S_W_EACTIVEL + S_W_EACTIVEML + S_VOTE + S_HL_NAWORK + S_HL_AWORKL + S_HLAWORKLTL + S_HLAWORKS



