---
title: "Replikaatio"
author: "Annika Lehmus-Sun"
output: html_document
---
#REPLIKOITAVA TUTKIMUS JA ANALYYSI
Tutkimus: anand et al. toimintamahdollisuuksien teoria, alkuperäinen julkaistu artikkeli analyysista löytyy täältä: [Anand et al.](http://philosophy.uchicago.edu/faculty/files/nussbaum/Capabilities%20and%20Well-Being%20Evidence%20Based%20on%20the%20Sen-Nussbaum%20Approach%20to%20Welfare.pdf)

#AINEISTO JA MUUTTUJAT
British household panel Survey [BHPS] vuosi 2000. Lisätietoa aineistosta löydät täältä: [BHPS 2000](https://www.iser.essex.ac.uk/bhps/documentation/pdf_versions/index.html) ja yleistä BHPS:stä: [British household panel survey](https://www.iser.essex.ac.uk/bhps)
Anand. et al. käyttivät analyysissaan seuraavia muuttujia: 

1. **S_HL_LIMIT** Does your health in any way limit your daily activities compared to most people of your age?
2. **S_HL_NOURISH** Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Eat meat, chicken, fish every second day) 
 + 2a.  Would you like to be able to eat meat, chicken, fish at least every second day, but must do without because you cannot afford it?
3. **S_H_LAC_MOVE** If you could choose, would you stay here in your present home or would you prefer to move somewhere else?
  + 3a. Even though you may not want to move) Do you expect you will move in the coming year?
5. **S_S_CAR** Do you normally have access to a car or van that you can use whenever you want to?
6. **S_H_CRIME** Does your accommodation have any of the following problems? Vandalism or crime in the area
7. **S_S_EDUCATE** Education
8. **S_W_CONCB**; **S_W_CONCL**; **S_W_CONCML** Have you recently been able to concentrate on whatever you’re doing (‘Better than usual’;‘Less than usual’;‘Much less than usual)
9. JGHQB Have you recently lost much sleep over worry?
10. JGHQE Have you recently felt constantly under strain? 
11.JGHQI Have you recently been feeling unhappy or depressed?
12. JGHQJ Have you recently been losing confidence in yourself? 
13. JGHQD Have you recently felt capable of making decisions about things? 
14. JGHQF Have you recently felt you couldn’t overcome your difficulties?
15. JGHQH Have you recently been able to face up to problems?
16. JHSCANB Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Pay for a week’s annual holiday away from home.
 + 16a. Would you like to be able to pay for a week’s annual holiday away from home, but must do without because you cannot afford it?
17. JHSCAND Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Buy new, rather than second hand, clothes.
 + 17a Would you like to be able to buy new, rather than second hand, clothes, but must do without because you cannot afford it?
18. JHSCANF Here is a list of things which people might have or do. Please look at this card and tell me which things you (and your household) have or do? Have friends or family for a drink or meal at least once a month
 +18a. Would you like to be able to have friends or family for a drink or meal at least once a month, but must do without because you cannot afford it?
19. JGHQK Have you recently been thinking of yourself as a worthless person? 
20. JGHQC Have you recently felt that you were playing a useful part in things?
21. JGHQL Have you recently been feeling reasonably happy, all things considered?
22. JGHQG Have you recently been able to enjoy your normal day- to-day activities?
23. JVOTE7 Did you vote in this (past) year’s general election?
24. JHLENDW Does your health keep you from doing some types of work?
25. JHLLTWA For work you can do, how much does your health limit the amount of work you can do?
26. **S_OALL** How dissatisfied or satisfied are you with your life overall?
27. **S_HEALTH** How dissatisfied or satisfied are you with your health?
28. **S_H_INCOME** How dissatisfied or satisfied are you with the income of your household?
29. **S_HOUSE** How dissatisfied or satisfied are you with your house/flat?
30. **S_PARTNER2** How dissatisfied or satisfied are you with your husband/ wife/partner?
31. **S_JOB2** How dissatisfied or satisfied are you with your job?
32. **S_SOCIAL** How dissatisfied or satisfied are you with your social life?
33. **S_QLEISURE** How dissatisfied or satisfied are you with the amount of leisure time you have?
34. **S_LEISURE** How dissatisfied or satisfied are you with the way you spend your leisure?

Where is the gender variable?? 
##Muuttujamuutokset
Muuttujamuunnokset, jotka ovat tehty Anand et. al.:in analyysin pohjalta ja mukaisesti löytyvät täältä: [muuttujamuunnokset](https://github.com/AnnikaLehmusSun/replikaatio/blob/master/data/muuttujamuunnokset.R)

###Puuttuvat tiedot
tämähän kannattaa nyt kirjata raporttiin – tutkimusta ei voi täysin varmasti toistaa, kun ei ole kerrottu mitä puuttuville
tiedoille on tehty, ja päättää itse miten etenet –eli varmaan tuo NA on loogisin oletus.

#REPLIKAATIO
```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(haven, ggplot2,knitr, pander,descr,foreign,dplyr,Hmisc,psych,GPArotation,plyr, dplyr, rmarkdown)
BHPS <- read.csv(file = "/Applications/replikaatio/data/BHPS_data.csv", sep=",", header =TRUE)
BHPS$X <- NULL
```
##Malli 1
Overall satisfaction regressed on elements of satisfaction (model 1) – females
C
D_NOJOB
D_NOPARTNER
S_HEALTH
S_HOUSE
S_HINCOME
S_PARTNER2
S_JOB2
S_SOCIAL
S_LEISURE
S_QLEISURE
```{r, echo=FALSE}
library(GGally)
library(ggplot2)
model1 <- lm(Points ~ Attitude + deep + Age, data = BHPS)
summary(model1)
```
##Malli 2
Overall satisfaction regressed on elements of satisfaction (model 1) – males
C
D_NOJOB
D_NOPARTNER
S_HEALTH
S_HOUSE
S_HINCOME
S_PARTNER2
S_JOB2
S_SOCIAL
S_LEISURE
S_QLEISURE
```{r}
model2 <- lm(Points ~ Attitude + deep + Age, data = learning2014)
summary(model2)
```
##Malli 3
Overall satisfaction regressed on elements of satisfaction and personality traits (model 2) – females
C
D_NOJOB
D_NOPARTNER
S_HEALTH
S_HOUSE
S_HINCOME
S_PARTNER2
S_JOB2
S_SOCIAL
S_LEISURE
S_QLEISURE
RESIDF_DNOJOB
RESIDF_DNOPARTNR
RESIDF_HEALTH
RESIDF_HOUSE
RESIDF_HINCOME
RESIDF_PARTNER
RESIDF_JOB
RESIDF_SOCIAL
RESIDF_LEISURE
RESIDF_QLEISURE
```{r}
model1 <- lm(Points ~ Attitude + deep + Age, data = learning2014)
summary(model1)
```
##Malli 4
Overall satisfaction regressed on elements of satisfaction and personality traits (model 2) – males
C
D_NOJOB
D_NOPARTNER
S_HEALTH
S_HOUSE
S_HINCOME
S_PARTNER2
S_JOB2
S_SOCIAL
S_LEISURE
S_QLEISURE
RESIDM_DNOJOB
RESIDM_DNOPARTNR
RESIDM_HEALTH
RESIDM_HOUSE
RESIDM_HINCOME
RESIDM_PARTNER
RESIDM_JOB
RESIDM_SOCIAL
RESIDM_LEISURE
RESIDM_QLEISURE
```{r}
model1 <- lm(Points ~ Attitude + deep + Age, data = learning2014)
summary(model1)
```
##Malli 5
Overall satisfaction regressed on capabilities and personality traits (model 3) – females
S_HL_LIMIT S_HL_NOURISH S_H_LAC_MOVE S_S_CAR
S_H_CRIME S_S_EDUCATE S_W_CONCB S_W_CONCL S_W_CONCML S_W_SLEEPN S_W_SLEEPM S_W_SLEEPMM S_W_STRAINN S_W_STRAINM S_W_STRAINMM S_W_DEPRESSN S_W_DEPRESSM S_W_DEPRESSMM S_W_CONFIDENTN S_W_CONFIDENTM S_W_CONFIDENTMM S_W_DECIDEM S_W_DECIDEL S_W_DECIDEML S_W_DIFFICULTN S_W_DIFFICULTM S_W_DIFFICULTMM S_W_FACEUPM S_W_FACEUPL S_W_FACEUPML S_S_HOLIDAY2 S_S_CLOTHES2 S_S_MEAL2 S_W_WORTHN S_W_WORTHM S_W_WORTHMM S_W_ROLEM, S_W_ROLEL S_W_ROLEML S_W_HAPPYM S_W_HAPPYL S_W_HAPPYML S_W_EACTIVEM S_W_EACTIVEL S_W_EACTIVEML S_VOTE
S_HL_PWORK S_HL_NAWORK S_HL_AWORKL S_HL_AWORKLTL S_HL_AWORKS RESIDF_DNOJOB RESIDF_DNOPARTNR RESIDF_HEALTH RESIDF_HOUSE RESIDF_HINCOME RESIDF_PARTNER RESIDF_JOB RESIDF_SOCIAL RESIDF_LEISURE RESIDF_QLEISURE
```{r}
model1 <- lm(Points ~ Attitude + deep + Age, data = learning2014)
summary(model1)
```
##Malli 6
Overall satisfaction regressed on capabilities and personality traits (model 3) – males
S_HL_LIMIT S_HL_NOURISH S_H_LAC_MOVE S_S_CAR
S_H_CRIME S_S_EDUCATE S_W_CONCB S_W_CONCL S_W_CONCML S_W_SLEEPN S_W_SLEEPM S_W_SLEEPMM S_W_STRAINN S_W_STRAINM S_W_STRAINMM S_W_DEPRESSN S_W_DEPRESSM S_W_DEPRESSMM S_W_CONFIDENTN S_W_CONFIDENTM S_W_CONFIDENTMM S_W_DECIDEM S_W_DECIDEL S_W_DECIDEML S_W_DIFFICULTN S_W_DIFFICULTM S_W_DIFFICULTMM S_W_FACEUPM S_W_FACEUPL S_W_FACEUPML S_S_HOLIDAY2 S_S_CLOTHES2 S_S_MEAL2 S_W_WORTHN S_W_WORTHM S_W_WORTHMM S_W_ROLEM, S_W_ROLEL S_W_ROLEML S_W_HAPPYM S_W_HAPPYL S_W_HAPPYML S_W_EACTIVEM S_W_EACTIVEL S_W_EACTIVEML S_VOTE
S_HL_PWORK S_HL_NAWORK S_HL_AWORKL S_HL_AWORKLTL S_HL_AWORKS RESIDF_DNOJOB RESIDF_DNOPARTNR RESIDF_HEALTH RESIDF_HOUSE RESIDF_HINCOME RESIDF_PARTNER RESIDF_JOB RESIDF_SOCIAL RESIDF_LEISURE RESIDF_QLEISURE
```{r}
model1 <- lm(Points ~ Attitude + deep + Age, data = learning2014)
summary(model1)
```
##Malli 7
```{r}
model1 <- lm(Points ~ Attitude + deep + Age, data = learning2014)
summary(model1)
```

#TULOKSET

#LÄHTEET

